Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

K-S statistic are obtained by finding the furthest vertical distance between the two CDFs as indicated by the arrows. The greater the distance, the more likely it is that two CDFs are from two different distributions so that it can be an indication that there is a change
on performance.
\begin{figure}[htb]
	\centering
	\includegraphics[width=0.4\textwidth]{resources/ch2/ks.png}
	\caption{CDF dari dua buah sampel, panah menunjukkan nilai statistik Kolmogorov-Smirnov \cite{wiki:ks-test}}
	\label{ks-example}
\end{figure}

>>>>

K-S statistic are obtained by finding the furthest vertical distance between the two CDFs as indicated by the arrows. The greater the distance, the more likely it is that two CDFs are from two different distributions so that it can be an indication that there has been a change on performance.
\begin{figure}[htb]
	\centering
	\includegraphics[width=0.4\textwidth]{resources/ch2/ks.png}
	\caption{CDF dari dua buah sampel, panah menunjukkan nilai statistik Kolmogorov-Smirnov \cite{wiki:ks-test}}
	\label{ks-example}
\end{figure}
